GO and KEGG Term Enrichment

### 2025-02-03 G85R GOandKEGGTermEnrichment.Rmd
fixed a warning

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')

@@

temp.FC = colnames(G85R.FC)
temp1 = temp.FC[grep(Geno1, temp.FC)]

if(Sex1 != Sex2){
  temp1 = temp1[intersect(grep(Sex1, temp1), grep(Sex2, temp1))]
  temp1 = temp1[grep(Geno1)]
}

if(Sex1 == Sex2){
  if(Geno1 == Geno2){
  temp1 = temp1[grep(setdiff(c("WT", "GR"), c(Geno1, Geno2)), temp1, invert = T)]
  }

  if(Geno1 != Geno2){
  temp1 = temp1[intersect(grep(Geno1, temp1), grep(Geno2, temp1))]
  }

  temp1 = temp1[intersect(grep(TKT1, temp1), grep(TKT2, temp1))]

  temp1 = temp1[grep(Sex1, temp1)]
}

FC = G85R.FC[temp1]
FDR = G85R.FC[temp1]

Variable.Condition = "GRFC" 
Control.Condition = "WTFC"
secondary.Variable.Condition = "GRMC"
secondary.Control.Condition = "WTMC"

comparison = paste0(Variable.Condition, 'v', Control.Condition)
secondary.comparison = paste0(secondary.Variable.Condition, 'v', secondary.Control.Condition)

if(length(intersect(comparison, names(A4V.comparekey))) == 1){
  FC = A4V.FC[,c(A4V.comparekey[comparison], A4V.comparekey[secondary.comparison])]
  FDR = A4V.FDR[,c(A4V.comparekey[comparison], A4V.comparekey[secondary.comparison])]
  mean.data = A4V.meancpm[,c(Variable.Condition, Control.Condition, 
                             secondary.Variable.Condition, secondary.Control.Condition)]
  metab.data = 'none'
}

if(length(intersect(comparison, names(G85R.comparekey))) == 1){
  FC = G85R.FC[,c(G85R.comparekey[comparison], G85R.comparekey[secondary.comparison])]
  FDR = G85R.FDR[,c(G85R.comparekey[comparison], G85R.comparekey[secondary.comparison])]
  mean.data = G85R.meancpm[,c(Variable.Condition, Control.Condition, 
                              secondary.Variable.Condition, secondary.Control.Condition)]
  metab.data = G85R.metab.comparekey[c(comparison, secondary.comparison)]
  if(G85R.metab.comparekey[c(comparison)] == G85R.metab.comparekey[c(secondary.comparison)]){
    metab.data = G85R.metab.comparekey[c(comparison)]
  }
}

subset = F

if(subset == T){
  geneset = biomarkers
  FC[setdiff(row.names(FC),geneset),] = 1 
  FDR[setdiff(row.names(FDR),geneset),] = 1 
}

@@

##Uses data from primary comparison
##point size is relative to mean expression in variable condition
volcano(FC, FDR, mean.data)

@@

##Uses data from primary comparison
##point size is relative to mean expression in variable condition
compare.genes(FC, FDR, mean.data)

```{r echo = F}
#library(heatmaply)
#hmdata = mean.data[geneset,]
#row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
#hmdata = na.omit(hmdata)

#heatmaply(hmdata,
#          scale = 'row',
#          Colv = F)

@@

##Uses data from primary comparison
##point size is relative to mean expression in variable condition
DEG.venn(FDR, FC)

@@

```{r echo = F, include = F}

####Uses sigDEGs from primary comparison
cat.data = Enrichment(FDR)

@@

##which ranks of categories to use
##a vector of numbers specifying which ranks to use
##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.
##can also just type 'sigs.only' 
usecats=c(1:20)
#usecats = 'sigs.only'

KEGG20(cat.data, FC, FDR, usecats)

@@

plotkegg.genes(specific.kegg, FC, FDR, mean.data)

@@

KEGG.diagram(PathwayID, FC, use, metab.data)

@@

comparekegg.genes(specific.kegg, FC, FDR, mean.data)

@@

GO20(cat.data, GO.ontology, FC, FDR, usecats)

@@

plotgo.genes(specific.go, FC, FDR, mean.data)

@@

comparego.genes(specific.go, FC, FDR, mean.data)

@@

##a parent category generated in the treemapPlot function
parent.category = 'membrane lipid biosynthetic process'

plotparentcat.genes(parent.category, FC, FDR, mean.data)

@@

compareparent.genes(parent.category, FC, FDR, mean.data)
##dot size is relative to the max FDR of either condition

>>>>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

@@

##Conditions for second comparison
Geno3 = "GR"
TKT3 = "C"
Sex3 = "M"

Geno4 = "WT"
TKT4 = "C"
Sex4 = "M"

source('/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R.GOandKEGGPlottingFunctions.R')

plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,
                      Sex1, Sex2, Sex3, Sex4,
                      TKT1, TKT2, TKT3, TKT4)

@@

##Uses data from primary comparison
##Plots genes with an FDR <= 0.05
##point size is relative to maximum mean expression in the two conditions

G85R.volcano(plot.data)

@@

##Uses data from primary comparison
##point size is relative to max mean expression in any condition
##grey points indicate less than 1 fold difference between the comparisons
G85R.compare.genes(plot.data)

@@

##Uses data from primary comparison
##point size is relative to mean expression in variable condition
G85R.DEG.venn(plot.data)

@@

```{r echo = F, include = F, warning = F}

####Uses sigDEGs from primary comparison
cat.data = G85R.Enrichment(plot.data)

@@

##which ranks of categories to use
##a vector of numbers specifying which ranks to use
##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.
##can also just type 'sigs' 
usecats=c(1:20)
#usecats = 'sigs'

G85R.KEGG20(cat.data, plot.data, usecats)

@@

G85R.plotkegg.genes(specific.kegg, plot.data)

@@

G85R.KEGG.diagram(PathwayID, plot.data, use, sigs.only = F)

@@

G85R.comparekegg.genes(specific.kegg, plot.data)

@@

G85R.GO20(cat.data, GO.ontology, plot.data, usecats)

@@

G85R.plotgo.genes(specific.go, plot.data)

@@

G85R.comparego.genes(specific.go, plot.data)

@@

##a parent category generated in the treemapPlot function
parent.category = 'neurogenesis'

G85R.plotparentcat.genes(parent.category, plot.data)

@@

G85R.compareparent.genes(parent.category, plot.data)
##dot size is relative to the max FDR of either condition
